Stellar Migration and Chemical Enrichment in the Milky Way Disc: A Hybrid Model

### 2021-08-04 chemev/MWbimodality/paper/draft3/comparison_observations.tex
migration paper referee response

% fig 7 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
\caption{[O/Fe]-[Fe/H] diagrams for 15 Galactic regions spanning five bins in 
$R_\text{gal}$ and three in~$\left|z\right|$. Each region has its own panel, 
with radial bins shown in columns denoted at the top, and with bins in 
$\left|z\right|$ shown in rows denoted in text in the middle column. For each 
region, we plot~$N$~= 10,000 points sampled from our simulated stellar 
populations predicted by our fiducial model, where the probability of 
sampling is proportional to the present-day mass of each stellar population. 
In all panels, points are colour-coded according to the Galactocentric radius 
of birth of the stellar population. For reference, we plot in a solid black 
line in all panels the gas-phase [O/Fe]-[Fe/H] track predicted by the same 
SFH in the~$R_\text{gal}$ = 8 kpc annulus, but with the post-processing 
migration model; this curve is the same in all panels. } 
\label{fig:ofe_feh_diagram} 
\end{figure*}

@@

The left panel of Fig.~\ref{fig:tracks} shows gas phase [O/Fe]-[Fe/H] 
evolutionary tracks at several radii assuming the inside-out SFH, using either 
our post-processing (dotted) or diffusion (solid) migration prescriptions 
(see~\S~\ref{sec:methods:migration} and Fig.~\ref{fig:migration_schema}). 
For the post-processing model the tracks are smooth and simply follow the 
predictions of one-zone GCE models with the parameters appropriate to each 
radius --- with post-processing, radial migration has no impact on the gas-phase 
evolution. 
However, some of the tracks in the diffusion model are notably 
different, especially at early times and large radii. 
These differences arise because radial migration can transport stars 
significantly over the timescale of SN Ia enrichment, as discussed in~\S 
\ref{sec:methods:h277}.
\par 
To demonstrate this point, the right panel of Fig.~\ref{fig:tracks} plots a 
proxy of the SN Ia rate\footnote{
	From our~\vice~outputs, the total time derivative of the Fe mass in a given 
	annulus can be obtained by its change across a single timestep. By then 
	subtracting the CCSN contribution (known exactly given our adopted yield 
	and the SFR), approximately correcting for recycling, and adding back that 
	which was lost to star formation and outflows, we obtain a simple estimate 
	of Fe production by SNe Ia. 
} as a function of time for the same 0.1 kpc rings plotted in the left panel. 
At large radii the sources for the diffusion model exhibit large fluctuations 
relative to the smooth predictions of the underlying one-zone models, as 
migration boosts or depletes the predicted number of SN Ia progenitors. 
The deficits or excesses in SN Ia rate in turn drive upward or downward 
deviations in [O/Fe] relative to the smooth model tracks in the left panel. 
As an extreme example, in the 15 kpc annulus the SN Ia rate is nearly zero for 
the first~$\sim$3 Gyr, and its resulting [O/Fe] track is nearly flat over this 
interval, even though the smooth model track has dropped from [O/Fe] = 0.45 to 
[O/Fe]~$\approx$ 0.2. 
Although we illustrate the SN Ia rates for only a handful of rings, we have 
found that the variations between nearby rings are highly correlated in our 
models, suggesting that regions of the Galaxy move coherently in 
[O/Fe]-[Fe/H] space; this lends further insight into the streak-like appearance 
of some sub-populations in Fig.~\ref{fig:ofe_feh_diagram}.

% fig 8
\begin{figure*} 
\centering 
\includegraphics[scale = 0.42]{tracks.pdf} 
\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
plane for our inside-out SFH with either post-processing (dotted lines) or 
diffusion (solid lines) migration models. We plot tracks for seven of our 
$\Delta\rgal$ = 100 pc rings, 
colour-coded according to their Galactocentric radius and denoted by the 
legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 13.2 
Gyr in X's for the diffusion model and points for the post-processing model. 
\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
using the total time-derivative of the Fe mass in a given annulus, calculated 
by subtracting the contribution from recycling and CCSN enrichment and adding 
back that lost to star formation and outflows. We show these rates for the 
same rings as in the left-hand panel, multiplying them by various prefactors 
to improve clarity. } 
\label{fig:tracks} 
\end{figure*}

@@

\citealp{Duong2019, Griffith2021}).

@@

Metallicity distribution functions (MDFs) and their variations with Galactic 
region are a core prediction of GCE models. 
We have computed distributions of [Fe/H] and [O/H] using abundances from the 
16th data release~\citep[DR16;][]{Ahumada2020, Joensson2020} of APOGEE 
\citep{Majewski2017}. 
Abundances are determined by the APOGEE Stellar Parameters and Chemical 
Abundances Pipeline (ASPCAP;~\citealp{Holtzman2015, GarciaPerez2016}). 
We restrict our sample to stars with effective temperatures of 4000 K 
$\leq T_\text{eff} \leq$~4600 K, surface gravities of 1.0~$\leq \log g \leq$ 
2.5, and signal-to-noise ratios of at least 100. 
These cuts ensure that our sample consists of stars on the upper red giant 
branch, luminous enough to cover all regions of the disc, while excluding red 
clump stars to avoid possible abundance offsets between these stars and stars 
on the giant branch. 
Our observational results are similar to those shown by~\citet{Hayden2015}, 
but we use a larger data set, more recent APOGEE observations, and [O/H] and 
[Fe/H] rather than [$\alpha$/H] and [M/H]. 
\par 
The left and right panels of Fig.~\ref{fig:mdf_3panel_fe} show [Fe/H] 
distributions from our fiducial inside-out model and the APOGEE data, 
respectively, in bins of~\rgal~and~\absz. 
The observed midplane distributions (\absz~$\leq$~0.5 kpc) show the striking 
phenomenon first noted by~\citet{Hayden2015}: a shift from a skew-negative form 
in the inner Galaxy to a skew-positive form in the outer Galaxy, with a roughly 
symmetric [Fe/H] distribution at the solar circle. 
The simulation reproduces this behaviour, confirming that realistic radial 
migration can explain the radial dependence of the MDF shape as conjectured by 
\citet{Hayden2015} and illustrated in a more idealized simulation by 
\citet{Loebman2016}. 
\par 
In detail, the MDFs are not as smooth at large~\rgal~as in the observations; 
they are not as skewed in the inner and outer disc either. 
Dots in the lower left panel mark the target metallicities implied by our 
$\eta(\rgal)$ prescription in equation~\refp{eq:eta_rgal}. 
The modes of the stellar MDFs track these targets quite closely, except at 
\rgal~= 13 - 15 kpc, where the migrated population is so large compared to the 
in-situ population that it reshapes the peak of the MDF as well as the tails. 
The model also predicts a continuing increase of the mode metallicity down to 
\rgal~= 3 - 5 kpc, while the observed mode is the same at 3 - 5 kpc and 5 - 7 
kpc. 
We do not view this as a serious discrepancy, as it could be reduced by a
moderate adjustment of the~$\eta(\rgal)$ recipe so that the metallicity 
gradient in these regions is flat. 
We have computed such a comparison case and find that it does indeed reproduce 
this observational result, though it still underpredicts the skewness at 
small~\rgal. 
Alternatively, the flattening of the observed gradient could be a consequence 
of more aggressive quenching of star formation than assumed in our models. 
The surface density of star formation~$\dot{\Sigma}_\star$ in the Milky Way 
is known to reach a maximum at~\rgal~$\approx$ 4 kpc and decline by a factor 
of a few at smaller radii (see Fig. 1 of~\citealp{Peek2009} and Fig. 2 
of~\citealp{Fraternali2012} and data therein). 
Early quenching could cutoff the MDF at high [O/H] and [Fe/H] if it happens 
before the ISM reaches equilibrium abundance. 
Visual inspection of Fig.~\ref{fig:tracks} suggests that this process should 
occur around~$T \approx$ 6 - 8 Gyr if the MDF is to peak at 
[Fe/H]~$\approx$~+0.2 - 0.3.

@@

Going up from the midplane, the observed MDFs for the four inner annuli 
(\rgal~< 11 kpc) shift to lower average metallicity, and they converge in 
location and in shape, being roughly symmetric at~\absz~= 0.5 - 1 kpc and 
mildly skew-positive at~\absz~= 1 - 2 kpc. 
Qualitatively, the simulation reproduces this shift of mean metallicity, change 
of shape, and convergence of distributions at different~\rgal, although the 
model does not account for the entirety of the effect. 
We consider this a significant success of this simulation-based approach 
because our GCE model is constructed and tuned in~\rgal~alone, so trends with 
\absz~follow from the combinations of age-metallicity trends, age-velocity 
trends arising from ``upside-down'' disc formation and dynamical heating, and 
correlations between radial migration and vertical energy. 
\citet{Freudenburg2017} showed that chemical evolution in a vertically settling 
gas disc could explain the MDF trend with~\absz~seen by APOGEE in the inner 
disc, and here we see similar behaviour in a more fully ab initio model. 
\citet{Bird2020} showed that the dynamics of the~\hsim~simulation leads to good 
agreement with the observed age-velocity relation, and here we show that 
this success extends qualitatively to the vertical trends of chemical 
abundances. 
\par 
Quantitatively, there are significant differences between the predicted and 
observed distributions above the midplane. 
The model MDFs from~\absz~= 0.5 - 1 kpc are narrower and more skewed than the 
observed MDFs, with higher median [Fe/H]. 
At~\absz~= 1 - 2 kpc, the predicted MDFs are not as strikingly converged as the 
observed MDFs. 
In both the data and the model, the high-\absz~MDFs for the 11 - 13 and 13 - 15 
kpc annuli remain closer to their midplane counterparts. 
The model [O/Fe]-[Fe/H] distributions in the outer Galaxy appear to show the 
imprint of a few large migration episodes (see Fig.~\ref{fig:ofe_feh_diagram}). 
The smoothness of the observed MDFs at these radii and their similarity across 
\absz~suggests a more vigorous stirring. 
\par 
Fig.~\ref{fig:mdf_3panel_o} plots distributions of [O/H] instead of [Fe/H]. 
The appearance is quite similar to Fig.~\ref{fig:mdf_3panel_fe}, which is 
unsurprising but non-trivial given the different timescales of CCSN and SN Ia 
enrichment. 
The agreement and disagreement between the model and data are similar, though 
the discrepancy for~\absz~= 0.5 - 1 kpc is somewhat clearer in [O/H]. 
The model's outer Galaxy MDFs are less irregular in [O/H] than in [Fe/H], an 
indication that some of the structure in the [Fe/H] distributions is caused by 
the large fluctuations in the SN Ia rate as seen in Fig.~\ref{fig:tracks}. 
We have confirmed this conjecture by computing [Fe/H] MDFs for the 
post-processing radial migration prescription, finding that they are indeed 
more smooth at~\rgal~= 11 kpc. 
\par 
The MDF predictions for our other SFH scenarios - constant SFR, late-burst, and 
outer-burst - are different in detail, but they show the same qualitative 
trends as those in Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}. 
Our findings on the radial and vertical trends of the MDF are also similar 
to those of~\citet{Loebman2016}, who use a galaxy simulation evolved from 
rotating gas in a dark matter halo rather than cosmological initial conditions. 
The qualitative similarity of our results across different models implies that 
the radial and vertical trends are a generic effect of radial migration, 
upside-down disc formation, and dynamical heating in a galaxy with realistic 
abundance gradients and time evolution.

@@

Fig.~\ref{fig:ofe_mdfs_insideout} compares our predicted [O/Fe] distributions 
in Galactic zones to those recently published by 
\citet{Vincenzo2021a}.\footnote{
	\citet{Vincenzo2021a} present [Mg/Fe] distributions in their figures, but 
	they have quantified the [O/Fe] as well, and we use the latter here. 
}
As in our~\S~\ref{sec:obs_comp:mdfs}, they use APOGEE DR16 with similar cuts on 
effective temperature, surface gravity, and signal-to-noise (see their~\S~2). 
They correct for observational scatter as well as age-dependent and (more 
importantly)~\absz-dependent selection in APOGEE to infer the intrinsic 
distribution of [O/Fe] in bins of [Fe/H] that would be found for an unbiased 
sample of long-lived disc stars. 
At a given~\rgal~and [Fe/H],~\citet{Vincenzo2021a} fit a model comprised of two 
Gaussians in [O/Fe], one each for the high-$\alpha$ and low-$\alpha$ 
populations.
The~\absz-dependence of the distribution follows from the empirical scale 
heights of these two populations, taken from~\citet{Bovy2016}. 
Dotted curves in Fig.~\ref{fig:ofe_mdfs_insideout} show these models integrated 
over the corresponding ranges in~\absz.

Solid histograms in Fig.~\ref{fig:ofe_mdfs_insideout} show distributions in 
0.4-dex bins of [O/Fe] for our fiducial inside-out model. 
For clarity we have chosen to focus our comparison on two bins of [Fe/H], one 
just above solar metallicity (0.0~$\leq$ [Fe/H]~$\leq$ 0.2) and one at 
sub-solar metallicity (-0.4~$\leq$ [Fe/H]~$\leq$ -0.2) where the bimodality of 
[O/Fe] is most pronounced. Results for our other models are qualitatively 
similar, and these two [Fe/H] bins illustrate the range of model successes and 
failure. 

@@

previously selected for investigation for its quiescent merger history 

@@

@@

\subsection{The Age-[$\alpha$/Fe] Relation} 
\label{sec:obs_comp:age_alpha} 
In this section, we assess the predicted age-[O/Fe] relations of our models, 
using the results of~\citet{Feuillet2019} as the observational benchmark. 
Their stellar age measurements are based on isochrone matching, 
using APOGEE DR14 stars for which parallax measurements are available 
from Gaia~\citep{Abolfathi2014, GaiaDR2}. 
With their spatial and quality cuts, the final sample consisted of 77,562 
stars. 
In bins of [O/Fe], they assume a Gaussian distribution of log age, fitting the 
mean (or equivalently, the median) and standard deviation to the stars in that 
bin. 
The choice of a Gaussian distribution is driven by simplicity, enabling 
estimates of mean and spread for data with significant age errors, but because 
our model predicts non-Gaussian log age distributions at fixed [O/Fe], the 
comparison to data is not free of nuance. 
We base most of our model comparisons below on the mass-weighted median age, 
simply denoting the 50th percentile of the mass-weighted age distribution of 
some subsample. 
\par

@@

When the SN Ia Fe production rate fluctuates downward, [O/Fe] fluctuates 
upward in the ISM, and the stars that form from it inherit such a composition. 
These stars then migrate to the solar annulus. 

@@

\citep{SilvaAguirre2018}. 

@@

in fact old stars ``rejuvenated'' by mergers or mass transfer events. 

@@

\citet{Weinberg2017} and~\citet{Johnson2020} proposed that young~$\alpha$-rich 
stars could arise in bursts of star formation that enhance the rate of CCSN 
enrichment. The explanation suggested here is in some sense the opposite: the 
stars are not so much~$\alpha$-rich as they are Fe-poor because of the 
deficit in SNe Ia events. 

@@

@@

While neither model reproduces the data perfectly, the agreement is better 
overall for the late-burst model, a difference that is more evident from 
looking at all four annuli rather than the solar neighbourhood alone. 
The late-burst of star formation reduces the median age of [Fe/H]~$\approx$ 0 
stars, typically by 1 - 2 Gyr. 
The median age of the highest metallicity stars increases because the 
enhanced pristine gas accretion that fuels the starburst (see Fig. 
\ref{fig:evol}) dilutes the ISM metallicity, an effect that is evident in the 
tracks for a given birth~\rgal~in the lower panels. 

@@

With reduced median age at [Fe/H]~$\approx$ 0 and increased median at 
[Fe/H] > 0.2, the late-burst model more consistently reproduces the C-shaped 
AMR that is the most striking qualitative feature of the observations. 

>>>>

% fig 8
\begin{figure*} 
\centering 
\includegraphics[scale = 0.42]{tracks.pdf} 
\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
plane for our inside-out SFH with either post-processing (dotted lines) or 
diffusion (solid lines) migration models. We plot tracks for seven of our 
$\delta\rgal$ = 100 pc rings, 
colour-coded according to their Galactocentric radius and denoted by the 
legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 13.2 
Gyr in X's for the diffusion model and points for the post-processing model. 
\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
using the total time-derivative of the Fe mass in a given annulus, calculated 
by subtracting the contribution from recycling and CCSN enrichment and adding 
back that lost to star formation and outflows. We show these rates for the 
same rings as in the left-hand panel, multiplying them by various prefactors 
to improve clarity. } 
\label{fig:tracks} 
\end{figure*}

@@

The left panel of Fig.~\ref{fig:tracks} shows gas phase [O/Fe]-[Fe/H] 
evolutionary tracks at several radii assuming the inside-out SFH, using either 
our post-processing (dotted) or diffusion (solid) migration prescriptions 
(see~\S~\ref{sec:methods:migration} and Fig.~\ref{fig:migration_schema}). 
For the post-processing model the tracks are smooth and simply follow the 
predictions of one-zone GCE models with the parameters appropriate to each 
radius --- with post-processing, radial migration has no impact on the gas-phase 
evolution. 
However, some of the tracks in the diffusion model are notably 
different, especially at early times and large radii. 
These differences arise because radial migration can transport stars 
significantly over the timescale of SN Ia enrichment, as discussed in~\S 
\ref{sec:methods:h277}.
To demonstrate this point, the right panel of Fig.~\ref{fig:tracks} plots a 
proxy of the SN Ia rate\footnote{
	From our~\vice~outputs, the total time derivative of the Fe mass in a given 
	annulus can be obtained by its change across a single timestep. By then 
	subtracting the CCSN contribution (known exactly given our adopted yield 
	and the SFR), approximately correcting for recycling, and adding back that 
	which was lost to star formation and outflows, we obtain a simple estimate 
	of Fe production by SNe Ia. 
} as a function of time for the same 0.1 kpc rings plotted in the left panel. 
At large radii the sources for the diffusion model exhibit large fluctuations 
relative to the smooth predictions of the underlying one-zone models, as 
migration boosts or depletes the predicted number of SN Ia progenitors. 
The deficits or excesses in SN Ia rate in turn drive upward or downward 
deviations in [O/Fe] relative to the smooth model tracks in the left panel. 
As an extreme example, in the 15 kpc annulus the SN Ia rate is nearly zero for 
the first~$\sim$3 Gyr, and its resulting [O/Fe] track is nearly flat over this 
interval, even though the smooth model track has dropped from [O/Fe] = 0.45 to 
[O/Fe]~$\approx$ 0.2. 
Although we illustrate the SN Ia rates for only a handful of rings, we have 
found that the variations between nearby rings are highly correlated in our 
models, suggesting that regions of the Galaxy move coherently in 
[O/Fe]-[Fe/H] space; this lends further insight into the streak-like appearance 
of some sub-populations in Fig.~\ref{fig:ofe_feh_diagram}. 

@@

\citealp{Duong2019, Griffith2021a}).

@@

@@

Metallicity distribution functions (MDFs) and their variations with Galactic 
region are a core prediction of GCE models. 
We have computed distributions of [Fe/H] and [O/H] using abundances from the 
16th data release~\citep[DR16;][]{Ahumada2020, Joensson2020} of APOGEE 
\citep{Majewski2017}. 
Abundances are determined by the APOGEE Stellar Parameters and Chemical 
Abundances Pipeline (ASPCAP;~\citealp{Holtzman2015, GarciaPerez2016}). 
We restrict our sample to stars with effective temperatures of 4000 K 
$\leq T_\text{eff} \leq$~4600 K, surface gravities of 1.0~$\leq \log g \leq$ 
2.5, and signal-to-noise ratios of at least 100. 
These cuts ensure that our sample consists of stars on the upper red giant 
branch, luminous enough to cover all regions of the disc, while excluding red 
clump stars to avoid possible abundance offsets between these stars and stars 
on the giant branch. 
Our observational results are similar to those shown by~\citet{Hayden2015}, 
but we use a larger data set, more recent APOGEE observations, and [O/H] and 
[Fe/H] rather than [$\alpha$/H] and [M/H]. 
The left and right panels of Fig.~\ref{fig:mdf_3panel_fe} show [Fe/H] 
distributions from our fiducial inside-out model and the APOGEE data, 
respectively, in bins of~\rgal~and~\absz. 
The observed midplane distributions (\absz~$\leq$~0.5 kpc) show the striking 
phenomenon first noted by~\citet{Hayden2015}: a shift from a skew-negative form 
in the inner Galaxy to a skew-positive form in the outer Galaxy, with a roughly 
symmetric [Fe/H] distribution at the solar circle. 
The simulation reproduces this behaviour, confirming that realistic radial 
migration can explain the radial dependence of the MDF shape as conjectured by 
\citet{Hayden2015} and illustrated in a more idealized simulation by 
\citet{Loebman2016}. 
In detail, the MDFs are not as smooth at large~\rgal~as in the observations; 
they are not as skewed in the inner and outer disc either. 
Dots in the lower left panel mark the target metallicities implied by our 
$\eta(\rgal)$ prescription in equation~\refp{eq:eta_rgal}. 
The modes of the stellar MDFs track these targets quite closely, except at 
\rgal~= 13 - 15 kpc, where the migrated population is so large compared to the 
in-situ population that it reshapes the peak of the MDF as well as the tails. 
The model also predicts a continuing increase of the mode metallicity down to 
\rgal~= 3 - 5 kpc, while the observed mode is the same at 3 - 5 kpc and 5 - 7 
kpc. 
We do not view this as a serious discrepancy, as it could be reduced by a
moderate adjustment of the~$\eta(\rgal)$ recipe so that the metallicity 
gradient in these regions is flat. 
We have computed such a comparison case and find that it does indeed reproduce 
this observational result, though it still underpredicts the skewness at 
small~\rgal. 
{\color{red} 
It's also possible that the differences at 3 - 5 kpc are due to stars 
associated with the Milky Way's strong bar, which~\citet{Bovy2019} demonstrate 
to be low metallicity (see their Fig. 5). 
With only a weak and transient bar in~\hsim, this is a dynamical effect not 
included in our models (see discussion in~\S~\ref{sec:methods:h277}). 
% It's also possible that the differences at 3 - 5 kpc are due to low metallicity 
% bar stars in the data~\citep[e.g. those observed by][]{Bovy2019}, a dynamical 
% effect not present in~\hsim~(see discussion in~\S~\ref{sec:methods:h277}). 
}
Alternatively, the flattening of the observed gradient could be a consequence 
of more aggressive quenching of star formation than assumed in our models. 
The surface density of star formation~$\dot{\Sigma}_\star$ in the Milky Way 
is known to reach a maximum at~\rgal~$\approx$ 4 kpc and decline by a factor 
of a few at smaller radii (see Fig. 1 of~\citealp{Peek2009} and Fig. 2 
of~\citealp{Fraternali2012} and data therein). 
Early quenching could cutoff the MDF at high [O/H] and [Fe/H] if it happens 
before the ISM reaches equilibrium abundance. 
Visual inspection of Fig.~\ref{fig:tracks} suggests that this process should 
occur around~$T \approx$ 6 - 8 Gyr if the MDF is to peak at 
[Fe/H]~$\approx$~+0.2 - 0.3. 
Going up from the midplane, the observed MDFs for the four inner annuli 
(\rgal~< 11 kpc) shift to lower average metallicity, and they converge in 
location and in shape, being roughly symmetric at~\absz~= 0.5 - 1 kpc and 
mildly skew-positive at~\absz~= 1 - 2 kpc. 
Qualitatively, the simulation reproduces this shift of mean metallicity, change 
of shape, and convergence of distributions at different~\rgal, although the 
model does not account for the entirety of the effect. 
We consider this a significant success of this simulation-based approach 
because our GCE model is constructed and tuned in~\rgal~alone, so trends with 
\absz~follow from the combinations of age-metallicity trends, age-velocity 
trends arising from ``upside-down'' disc formation and dynamical heating, and 
correlations between radial migration and vertical energy. 
\citet{Freudenburg2017} showed that chemical evolution in a vertically settling 
gas disc could explain the MDF trend with~\absz~seen by APOGEE in the inner 
disc, and here we see similar behaviour in a more fully ab initio model. 
\citet{Bird2021} showed that the dynamics of the~\hsim~simulation leads to good 
agreement with the observed age-velocity relation, and here we show that 
this success extends qualitatively to the vertical trends of chemical 
abundances. 
Quantitatively, there are significant differences between the predicted and 
observed distributions above the midplane. 
The model MDFs from~\absz~= 0.5 - 1 kpc are narrower and more skewed than the 
observed MDFs, with higher median [Fe/H]. 
At~\absz~= 1 - 2 kpc, the predicted MDFs are not as strikingly converged as the 
observed MDFs. 
In both the data and the model, the high-\absz~MDFs for the 11 - 13 and 13 - 15 
kpc annuli remain closer to their midplane counterparts. 
The model [O/Fe]-[Fe/H] distributions in the outer Galaxy appear to show the 
imprint of a few large migration episodes (see Fig.~\ref{fig:ofe_feh_diagram}). 
The smoothness of the observed MDFs at these radii and their similarity across 
\absz~suggests a more vigorous stirring. 
Fig.~\ref{fig:mdf_3panel_o} plots distributions of [O/H] instead of [Fe/H]. 
The appearance is quite similar to Fig.~\ref{fig:mdf_3panel_fe}, which is 
unsurprising but non-trivial given the different timescales of CCSN and SN Ia 
The agreement and disagreement between the model and data are similar, though 
the discrepancy for~\absz~= 0.5 - 1 kpc is somewhat clearer in [O/H]. 
The model's outer Galaxy MDFs are less irregular in [O/H] than in [Fe/H], an 
indication that some of the structure in the [Fe/H] distributions is caused by 
the large fluctuations in the SN Ia rate as seen in Fig.~\ref{fig:tracks}. 
We have confirmed this conjecture by computing [Fe/H] MDFs for the 
post-processing radial migration prescription, finding that they are indeed 
more smooth at~\rgal~= 11 kpc. 
The MDF predictions for our other SFH scenarios - constant SFR, late-burst, and 
outer-burst - are different in detail, but they show the same qualitative 
trends as those in Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}. 
Our findings on the radial and vertical trends of the MDF are also similar 
to those of~\citet{Loebman2016}, who use a galaxy simulation evolved from 
rotating gas in a dark matter halo rather than cosmological initial conditions. 
The qualitative similarity of our results across different models implies that 
the radial and vertical trends are a generic effect of radial migration, 
upside-down disc formation, and dynamical heating in a galaxy with realistic 
abundance gradients and time evolution.

@@

Fig.~\ref{fig:ofe_mdfs_insideout} compares our predicted [O/Fe] distributions 
in Galactic zones to those recently published by 
\citet{Vincenzo2021a}.\footnote{
	\citet{Vincenzo2021a} present [Mg/Fe] distributions in their figures, but 
	they have quantified the [O/Fe] as well, and we use the latter here. 
}
As in our~\S~\ref{sec:obs_comp:mdfs}, they use APOGEE DR16 with similar cuts on 
effective temperature, surface gravity, and signal-to-noise (see their~\S~2). 
They correct for observational scatter as well as age-dependent and (more 
importantly)~\absz-dependent selection in APOGEE to infer the intrinsic 
distribution of [O/Fe] in bins of [Fe/H] that would be found for an unbiased 
sample of long-lived disc stars. 
At a given~\rgal~and [Fe/H],~\citet{Vincenzo2021a} fit a model comprised of two 
Gaussians in [O/Fe], one each for the high-$\alpha$ and low-$\alpha$ 
populations.
The~\absz-dependence of the distribution follows from the empirical scale 
heights of these two populations, taken from~\citet{Bovy2016}. 
Dotted curves in Fig.~\ref{fig:ofe_mdfs_insideout} show these models integrated 
over the corresponding ranges in~\absz. 
\par 
Solid histograms in Fig.~\ref{fig:ofe_mdfs_insideout} show distributions in 
0.04-dex bins of [O/Fe] for our fiducial inside-out model. 
For clarity we have chosen to focus our comparison on two bins of [Fe/H], one 
just above solar metallicity (0.0~$\leq$ [Fe/H]~$\leq$ 0.2) and one at 
sub-solar metallicity (-0.4~$\leq$ [Fe/H]~$\leq$ -0.2) where the bimodality of 
[O/Fe] is most pronounced. Results for our other models are qualitatively 
similar, and these two [Fe/H] bins illustrate the range of model successes and 
failure.

@@

previously selected for investigation because of its quiescent merger history 

@@

{\color{red} 
\citet{Mackereth2018} find similar conclusions in a sample of 133 Milky 
Way-like galaxies from the EAGLE simulation.
} 

@@

\subsection{The Age-[$\alpha$/Fe] Relation} 
\label{sec:obs_comp:age_alpha}

In this section, we assess the predicted age-[O/Fe] relations of our models, 
using the results of~\citet{Feuillet2019} as the observational benchmark. 
Their stellar age measurements are based on isochrone matching, 
using APOGEE DR14 stars for which parallax measurements are available 
from Gaia~\citep{Abolfathi2014, GaiaDR2}. 
With their spatial and quality cuts, the final sample consisted of 77,562 
stars. 
In bins of [O/Fe], they assume a Gaussian distribution of log age, fitting the 
mean (or equivalently, the median) and standard deviation to the stars in that 
bin. 
The choice of a Gaussian distribution is driven by simplicity, enabling 
estimates of mean and spread for data with significant age errors, but because 
our model predicts non-Gaussian log age distributions at fixed [O/Fe], the 
comparison to data is not free of nuance. 
We base most of our model comparisons below on the mass-weighted median age, 
simply denoting the 50th percentile of the mass-weighted age distribution of 
some subsample. 

@@

% When the SN Ia Fe production rate fluctuates downward, [O/Fe] fluctuates 
% upward in the ISM, and the stars that form from it inherit such a composition. 
% These stars then migrate to the solar annulus. 
% These stars can then migrate to the solar annulus. 
{\color{red} 
SNe Ia account for~$\sim$60\% of the Fe production at all metallicities 
in our models (see discussion in~\S~\ref{sec:methods:yields}). 
Visual inspection of Fig.~\ref{fig:tracks} indicates that the SN Ia rate can 
vary by as much as a factor of~$\sim$3 at~$\rgal\gtrsim$~9 kpc in our models, 
sometimes more in extreme cases, simply because their progenitors are 
migrating; this corresponds to variability as large as~$\sim$40\% in the total 
Fe enrichment rate if everything else is constant. 
This variability can arise in part out of efficient radial migration moving 
stars away from their birth radii faster than the SN Ia timescale as well as 
the combination of the long tail of the SN Ia DTD and migration on longer 
timescales (see discussion at the end of~\S~\ref{sec:methods:h277}). 
The [$\alpha$/Fe] ratio at a given time is approximately determined by the 
ratio of core collapse to type Ia supernova events occurring over the previous 
depletion time~\citep{Weinberg2017}, which can be short in the outer Galaxy in 
our models due to the substantial outflows at these radii (see discussion 
in~\S~\ref{sec:methods:outflows}). 
Consequently, when the SN Ia Fe production rate fluctuates downward, [O/Fe] 
fluctuates upward in the ISM. 
In a starburst event, the ISM becomes~$\alpha$-enhanced because the CCSN rate 
increases~\citep{Johnson2020}. 
The explanation suggested here is in some sense the opposite: the ISM 
becomes not necessarily~$\alpha$-rich but Fe-poor because of fewer SNe Ia. 
The stars that form inherit such a composition and can then migrate to 
the solar annulus, and our models predict the variability to be sufficiently 
large to explain the high [$\alpha$/Fe] ratios seen in APOGEE. 
}

@@

\citep{Martig2015, Jofre2016, Izzard2018, SilvaAguirre2018}. 

@@

in fact old stars ``rejuvenated'' by mergers or mass transfer events 
{\color{red} 
as postulated by~\citet{Jofre2016} and~\citet{Izzard2018}. 
In a sample of four young~$\alpha$-enhanced stars observed with Gemini-GRACES, 
\citet{Yong2016} find that two (possibly three) of them show evidence of a 
debris disc, indicative of previous interactions with a binary companion. 
} 

@@

% \citet{Weinberg2017} and~\citet{Johnson2020} proposed that
% young~$\alpha$-rich stars could arise in bursts of star formation that 
% enhance the rate of CCSN enrichment. 
% The explanation suggested here is in some sense the opposite: the 
% stars are not so much~$\alpha$-rich as they are Fe-poor because of the 
% deficit in SNe Ia events. 
{\color{red} 
We clarify that this result does not refute the previously suggested mass 
transfer origin; this mechanism explains the truly young, 
intrinsically~$\alpha$-enhanced stars which appear to make up a portion of the 
young~$\alpha$-rich population separate from those which formed via mass 
transfer~\citep{Yong2016, Hekker2019}. 
}

@@

{\color{red} 
They have a broad distribution in metallicity spanning from [Fe/H]~$\approx-1$ 
to~$\sim$solar, with multiple peaks indicative of separate sub-populations. 
Although small sample sizes have prevented the detailed analaysis of 
the [Fe/H] distribution of the young~$\alpha$-rich population, this 
qualitatively agrees with the findings of~\citet{SilvaAguirre2018} (see their 
Figs. 8 and 10) and~\citet{Miglio2021} (see their Fig. 5). 
However, a direct comparison to data is not free of nuance, because the 
young~$\alpha$-rich stars which formed via mass transfer likely outnumber those 
which are intrinsically young~\citep{Miglio2021}. 
} 

@@

% While neither model reproduces the data perfectly, the agreement is better 
% overall for the late-burst model, a difference that is more evident from 
% looking at all four annuli rather than the solar neighbourhood alone. 
{\color{red} 
At~\rgal~= 5 - 7 kpc, the inside-out model overpredicts the ages of solar and 
sub-solar metallicity stars, an issue which is mitigated by the late-burst 
model. 
The late-burst of star formation reduces the median age of these stars, 
typically by 1 - 2 Gyr, simply because more young stars form with the burst 
than without. 
The late-burst model also more convincingly reproduces the C-shaped AMR, the 
most striking qualitative feature of the observations. 
} 
The median age of the highest metallicity stars increases because the enhanced 
pristine gas accretion that fuels the starburst (see Fig.~\ref{fig:evol}) 
dilutes the ISM metallicity, an effect that is evident in the tracks for a 
given birth~\rgal~in the lower panels. 

@@

{\color{red} 
Both the increase in ages for the most metal-rich stars and decrease in ages 
for solar and sub-solar metallicity stars contribute to the late-burst model 
reproducing this C-shape better than the inside-out model. 
The top two rows of Fig.~\ref{fig:age_oh_comparison} in 
Appendix~\ref{sec:age_oh_relation} present the same comparison for the 
age-[O/H] relation, which is unaffected by SN Ia enrichment. 
The late-burst model improves upon the inside-out model there for the same 
reasons as in age-[Fe/H], but perhaps more clearly when comparing bin-by-bin. 
Although none of these models reproduce the data perfectly, the detailed form 
of the AMR in our models is sensitive to the nature of the recent starburst or 
lackthereof, and its true form was likely more complicated than our 
} 
% The late-burst of star formation reduces the median age of [Fe/H]~$\approx$ 0 
% stars, typically by 1 - 2 Gyr. 
% The median age of the highest metallicity stars increases because the 
% enhanced pristine gas accretion that fuels the starburst (see Fig. 
% \ref{fig:evol}) dilutes the ISM metallicity, an effect that is evident in the 
% tracks for a given birth~\rgal~in the lower panels. 
% Stars from the inner Galaxy that form during the burst do so at roughly solar 
% metallicity rather than appearing in the [Fe/H] = 0.2 - 0.5 bins. 
% With reduced median age at [Fe/H]~$\approx$ 0 and increased median at 
% [Fe/H] > 0.2, the late-burst model more consistently reproduces the C-shaped 
% AMR that is the most striking qualitative feature of the observations. 
